Data Synthesis Plan (Meta-Analysis)

### 2024-11-21 analysis_plan.qmd
Grateful report link on analysis plan

Statistical analysis of the data extracted will be performed in R, (v 4.3.3; R Core Team, https://www.r-project.org/) and RStudio (v 2023.06.1; Posit, https://posit.co/). All code utilised for data preparation and analyses are available in the corresponding GitHub repository <https://github.com/jamessteeleii/pcos_ree_meta>. We cite all software and packages used in the analysis pipeline using the `grateful` package [@rodriguez-sanchezGratefulFacilitateCitation2023] which can be seen here: [ADD LINKS](ADD LINK).

>>>>

Statistical analysis of the data extracted will be performed in R, (v 4.3.3; R Core Team, https://www.r-project.org/) and RStudio (v 2023.06.1; Posit, https://posit.co/). All code utilised for data preparation and analyses are available in the corresponding GitHub repository <https://github.com/jamessteeleii/pcos_ree_meta>. We cite all software and packages used in the analysis pipeline using the `grateful` package [@rodriguez-sanchezGratefulFacilitateCitation2023] which can be seen here: [https://github.com/jamessteeleii/pcos_ree_meta/blob/main/grateful-report.pdf](https://github.com/jamessteeleii/pcos_ree_meta/blob/main/grateful-report.pdf).
